Predicting FOMC Actions using ML and NLP

### 2019-05-04 presentation/paper.tex
update

% Document Formatting Packages:
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\newcommand{\vertSpace}[1]{\vspace{3mm}}

@@

In addition, because this is a binary classification problem, we also exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression without any regularization.  \vertSpace

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lass_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_reg_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/NB_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_accuracy_more iterations".pdf}
\end{center}
\end{figure}

\vspace{5cm}

Based on previous research that applied Naive Bayes to analyzing FOMC transcripts \cite{stanford} ML models performed better with N-grams and performance peaked at tri-grams for Naive Bayes.  In our models, we found that N-grams of greater N saw greater accuracy and lower standard deviation.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_f1".pdf}
\end{center}
\end{figure}

As seen in the graphs above, the Logistic Lasso regression performs the best out of the four basic models.

\subsection{Neural Network} 
% Bibliography
%-----------------------------------------------------------------
\begin{thebibliography}{99}

>>>>

% Document Formatting Packages:
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\newcommand{\vertSpace}[1]{\vspace{3mm}}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lass_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_reg_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/NB_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_accuracy_more iterations".pdf}
\end{center}
\end{figure}

In our search for the optimal model, we tested different strategies for feature selection, namely different size Ngrams and document stacking (i.e., combining the minutes, statements, and speeches for a meeting into one document).

\subsubsection{Ngrams}

For Ngrams, based on previous research analyzing FOMC transcripts \cite{stanford} with ML models, tri-grams and Naive Bayes performed the best for classifying the outcome of an FOMC meeting.  In line with that research, we found that N-grams of greater N generally resulted in greater accuracy and lower standard deviation.  \vertSpace

We observed that the optimal number of Ngrams for Logistic Lasso, Logistic regression, and SVM was between three to seven Ngrams.  The performance of the three models based on F1 score started to drop significantly with Ngrams greater than seven.  However, we observed that performance (F1 score) for Naive Bayes increased with larger Ngrams.  Please refer to charts below for an illustration of the performance (F1 score) of the models with Ngrams between one and ten.

\begin{figure}[H]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_f1".pdf}
\end{center}
\end{figure}

We observed that the Logistic regression with L1 penalty (i.e. Logistic Lasso) performed the best for Ngrams between one and ten and we attribute this to the model being well suited for the binary classification problem.  We exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression without any regularization.  \vertSpace

@@

\subsubsection{Stacked Documents}

In our research, we found that reducing the number of features through combining documents for each FOMC meeting into one and increasing Ngram size had a positive impact on accuracy for most of our models. \vertSpace

We created and tested 'super features' through stacking documents and increasing Ngrams, and we observed steadily increasing F1 performance for most of our simple models (except Logistic Lasso) and the verious Neural Net models we created.  Below is a snapshot of the results:

\begin{figure}[H]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1_stacked".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_f1_stacked".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1_stacked".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_f1_stacked".pdf}
\end{center}
\end{figure}

\textbf{Neural Network}

\begin{figure}[H]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_20_10_5_f1_stacked".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_40_40_40_f1_stacked".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_40_40_f1_stacked".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_40_f1_stacked".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_80_f1_stacked".pdf}
\end{center}
\end{figure}

\subsection{Neural Network}

% Bibliography
%-----------------------------------------------------------------
\begin{thebibliography}{99}
